Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data

### 2021-07-27 Manuscript/05-Discussion.Rmd
Revise conclusion

# Discussion

@@

In the manuscript, we describe the implementation of ssGAM-NM using EM-IRLS. Nevertheless, EM-IRLS are not limited to fitting ssGAM-NM. Other spike-and-slab prior can be fitted with EM-IRLS as well, e.g. mixture t-distribution, and mixture double exponential distributions. @Yi2012 demonstrated that t prior and double exponential prior can be seen hierarchical normal priors,
$$
\begin{aligned}
\beta_i \sim N(0, \tau^2_i),\\
\tau^2_i \sim Inv-\chi^2(v, s^2_j) \text{ or } \tau^2_i \sim Gamma(1, s^2/2)
\end{aligned}
$$
with $\tau^2$ integrated out analytically. Hence, the EM-IRLS can be easily applied to those two additional mixture priors. One of the advantage of using mixture $t$ prior over mixture normal prior is that $t$ distributions with low degree of freedom, e.g. $v=1$, have heavier tail than the normal distribution, which is also a special case of $t$ distribution when $v=\infty$. The heavier tails help to obtain posteriors that concentrated around the true nonzero coefficients at optimal rates. [@Rockova2014a]

>>>>

# Discussion
In the paper, we described a novel generalized additive model using Bayesian hierarchical priors, particularly the proposed spike-and-slab spline prior for bi-level functional selection. Meanwhile, we introduced two optimization based algorithms for model fitting. The algorithms can be easily scale up to address high-dimensional data analysis in a computational efficient manner, but also provide naive inferential supports for many commonly used hierarchical priors in the analyses that the sparse assumption is weak or not necessary. Via simulations, we demonstrated that the proposed model provides as good, if not better, prediction performance compared to some state-of-the-art non-linear modeling devices. Compared another newly developed high-dimensional Bayesian GAM that emphasize computational efficiency [@Bai2021], the proposed model provides flexibility to address bi-level functional selection and inferential support while maintaining the same level of prediction accuracy.

For transnational science purpose, the

Compare to previous Bayesian GAMs, the proposed model greatly increases the scalability to be applied in high-dimensioanl data analyses, while addressing the bi-level selection problem [@Bai2021].

the implementation of ssGAM-NM using EM-IRLS. Nevertheless, EM-IRLS are not limited to fitting ssGAM-NM. Other spike-and-slab prior can be fitted with EM-IRLS as well, e.g. mixture t-distribution, and mixture double exponential distributions. @Yi2012 demonstrated that t prior and double exponential prior can be seen hierarchical normal priors,
$$
\begin{aligned}
\beta_i \sim N(0, \tau^2_i),\\
\tau^2_i \sim Inv-\chi^2(v, s^2_j) \text{ or } \tau^2_i \sim Gamma(1, s^2/2)
\end{aligned}
$$
with $\tau^2$ integrated out analytically. Hence, the EM-IRLS can be easily applied to those two additional mixture priors. One of the advantage of using mixture $t$ prior over mixture normal prior is that $t$ distributions with low degree of freedom, e.g. $v=1$, have heavier tail than the normal distribution, which is also a special case of $t$ distribution when $v=\infty$. The heavier tails help to obtain posteriors that concentrated around the true nonzero coefficients at optimal rates. [@Rockova2014a]

@@
